### 2010-02-04 doc/manuals/configuration/configuration_manual.tex
Added ARC PDP and Delegation PDP

\subsubsection{X.509 Token}\label{sec:x509token-shc}
The X.509 Token Security Handler processes information in the SOAP Header
stored according to "Web Services Security X.509 Token Profile 1.0"
\cite{ws-security-usernametoken}. The plugin name of this Security Handler
is \texttt{x509token.handler} and it resides in \texttt{arcshc} loadable
module.

@@

%\subsubsection{SAML Token}% samltoken.handler
%\subsubsection{SAML Single Sign-On}% saml2ssoassertionconsumer.handler

\subsection{Policy Decision Points}\label{sec:Policy Decision Points}

>>>>

\subsubsection{X.509 Token}\label{sec:x509token-shc}
The X.509 Token Security Handler processes information in the SOAP Header
stored according to "Web Services Security X.509 Token Profile 1.0"
\cite{ws-security-x509token}. The plugin name of this Security Handler
is \texttt{x509token.handler} and it resides in \texttt{arcshc} loadable
module.

@@

\subsubsection{SAML Token}

\subsubsection{SAML Single Sign-On}

\subsection{Policy Decision Points}\label{sec:Policy Decision Points}
The Policy Decision Point component is responsible for applying particular
policy or any kind of authorization evaluation algorithm to properties 
of the message and providing authorization decision which then used by
other components - usually by the Security Handlers implementing 
functionality of Policy Enforcement Point.

\subsubsection{Allow}
This PDP always returns positive result. Its plugin name is \texttt{allow.pdp}
and it resides in \texttt{arcshc} loadable module.

\subsubsection{Deny}
This PDP always returns negative result. Its plugin name is \texttt{deny.pdp}
and it resides in \texttt{arcshc} loadable module.

\subsection{Simple List}
This PDP matches X.509 subject of client certificate to list of predefined values.
Its plugin name is \texttt{simplelist.pdp} and it resides in \texttt{arcshc} loadable
module.

Multiple configuration elements \texttt{DN} specify accepted subjects. Also attribute
\texttt{location} may be used to point to a file containing list of subjects, one
per line. If client's subject is not listed neither in \texttt{DN} nor in 
\texttt{location} PDP returns negative result. Otherwise result is positive. Below is
configuration example for simple authorization by grid-mapfile:
\begin{lstlisting}[language=xml]
...
    <PDP name="simplelist.pdp" location="/etc/grid-security/grid-mapfile">
      <DN>/O=Grid/O=NorduGrid/CN=Service Admin</DN>
    </PDP>
...
\end{lstlisting}

\subsubsection{ARC}\label{sec:arc-pdp}
This plugin applies authorization policy written in ARC Policy language to attributes
of the message. Its plugin name is \texttt{arc.pdp} and it resides in \texttt{arcshc}
loadable module. For more information about ARC Policy language please "Security 
Framework of ARC NOX" \cite{arc1-sec}.

The configuration element \texttt{PolicyStore} specifies locations of policy. Its
\texttt{Location} subelement provides path to file storing policy. Also policy can be 
directly embedded into configuration by using \texttt{Policy} configuration element.

The \texttt{PolicyCombiningAlg} element specifies how results from multiple policies
are combined. For detailed explanation please refer to \cite{arc1-sec}.

It is also possible to limit number of message attributes which are matched to policy
using \texttt{Filter} configuration element. This may be needed to achieve better
evaluation performance. The multiple subelements \texttt{Select} and \texttt{Reject}
allow to either use only specific attributes or remove specific attributes. If neither 
\texttt{Select} not \texttt{Reject} are specified then all attribites are used.

Example of simple ARC PDP reading policy from external file is below:
\begin{lstlisting}[language=xml]
...
    <PDP name="arc.pdp">
      <PolicyStore>
        <Location>/etc/grid-security/policy.xml</Location>
      </PolicyStore>
    </PDP>
...
\end{lstlisting}

\subsubsection{GACL}

\subsubsection{XACML}

\subsubsection{Delegation}\label{sec:delegation-pdp}
This plugin applies authorization policy written in ARC Policy language and obtained
from cahin of X.509 Proxy Certificates of client to attributes of the message. Its 
plugin name is \texttt{delegation.pdp} and it resides in \texttt{arcshc} loadable module.

Functionality wise it is very similar to ARC PDP described in section \ref{sec:arc-pdp}
but uses policy internally obtained from message. Hence it has only \texttt{Filter}
configuration element.

For detailed explanation how policy document is embedded into X.509 Proxy Certificate 
please refer to \cite{arc1-sec}.

\subsubsection{Service Invoker}
